% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
% (c) 2012 Joshua J Hamilton <joshamilton@gmail.com>
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{verbatim}
\usepackage{fancyhdr}
\usepackage{array}
\usepackage{lastpage}
\usepackage{etaremune}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}

% Define custom date format
\usepackage{datetime}
\newdateformat{myDate}{\monthname[\THEMONTH] \THEYEAR}

%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

%\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
%\setlength{\oddsidemargin}{-0.25in}
%\setlength{\paperheight}{11in}
%\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
%\setlength{\textheight}{9in}
%\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-0.1in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{
  \setlength{\FrameSep}{\outerbordwidth}
\setlength{\fboxsep}{0pt}
\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.262in][l]{\large #1} \vphantom{p\^{E}}}}}}
  }
  \vspace{-5pt}
}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{6in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

% Place information in the footer
\fancypagestyle{plain}{%
\fancyhf{} % clear all header and footer fields
\fancyfoot[L]{Hamilton CV}
\fancyfoot[C]{\thepage\ of \pageref*{LastPage}}
\fancyfoot[R]{Last revised: \myDate\today}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength\footskip{0.5in}
}
\pagestyle{plain}

%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Joshua J. Hamilton}  \\
Department of Bacteriology \\
University of Wisconsin-Madison & \emph{E-mail}: jjhamilton2@wisc.edu \\
5525 Microbial Sciences Building & \emph{Office}: 608-890-2858 \\
1550 Linden Drive & \emph{Cell}: 913-269-7789 \\
Madison, WI 53706 & \emph{Web}: \url{http://joshamilton.net} \\
\end{tabular*}
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education and Academic Positions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item
		\ressubheading{University of Wisconsin-Madison (UW-Madison)}{Madison, WI}{Postdoctoral Associate, Department of Bacteriology}{2014-present}
		\begin{itemize}
			\resitem{Advisor: Katherine D. McMahon}
		\end{itemize}
	\item
		\ressubheading{UW-Madison}{Madison, WI}{Ph.D., Chemical Engineering}{2009-2014}
		\begin{itemize}
			\resitem{Advisor: Jennifer L. Reed}
		\end{itemize}
	\item
		\ressubheading{Case Western Reserve University (CWRU)}{Cleveland, OH}{B.S., Chemical Engineering}{2005-2009}
		\begin{itemize}
			\resitem{\emph{Summa cum laude}}
		\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Fellowships}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2pt}
\begin{center}\begin{tabular*}{6.1in}{l@{\extracolsep{\fill}}r}
	\multicolumn{2}{c}{U.S. Department of Agriculture (USDA-NIFA), Postdoctoral Fellowship\cftdotfill{\cftdotsep}2015-present}\\
%	\multicolumn{2}{c}{Best Poster Award, COBRA 2014\cftdotfill{\cftdotsep}2014}\\	
	\multicolumn{2}{c}{National Science Foundation, Graduate Research Fellowship \cftdotfill{\cftdotsep}2010-2014}\\
%	\multicolumn{2}{c}{National Science Foundation, Graduate Research Fellowship (Honorable Mention) \cftdotfill{\cftdotsep}2009}\\
%	\multicolumn{2}{c}{U.S. Department of Energy Office of Science, Graduate Research Fellowship (Finalist) \cftdotfill{\cftdotsep}2009}\\	
	\multicolumn{2}{c}{UW-Madison, Bird, Stewart, and Lightfoot Distinguished Graduate Fellowship\cftdotfill{\cftdotsep}2009-2010}\\	
%	\multicolumn{2}{c}{CWRU, Robert J. Adler Award\cftdotfill{\cftdotsep}2009}\\	
%	\multicolumn{2}{c}{CWRU, Albert W. Smith Award\cftdotfill{\cftdotsep}2009}\\	
%	\multicolumn{2}{c}{CWRU, Outstanding Supplemental Instruction Leader\cftdotfill{\cftdotsep}2008}\\			
%	\multicolumn{2}{c}{Tau Beta Pi, Ohio Alpha Chapter\cftdotfill{\cftdotsep}2006}\\		
\vphantom{E}
\end{tabular*}\end{center}\vspace*{-16pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Manuscripts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{etaremune}[itemsep=-2pt]
	\item \textbf{Hamilton JJ}, Garcia SL, Brown BS*, Oyserman BO, Moya F, Bertilsson S, Malmstrom RR, Forest KT, and KD McMahon. \emph{Metabolic Network Analysis and Metatranscriptomics of a Cosmopolitan and Streamlined Freshwater Lineage}. bioRxiv. \href{https://doi.org/10.1101/106856}{doi:10.1101/106856}.
	\item Garcia SL, Buck M, \textbf{Hamilton JJ}, Wurzbacher C, Rosenblad MA, McMahon KD, Grossart HP, Warnecke F, and A Eiler. \emph{Model communities hint to promiscuous metabolic linkages between ubiquitous free-living freshwater bacteria}. bioRxiv. \href{https://doi.org/10.1101/103838}{doi:10.1101/103838}.
%	\item Dwulit-Smith JR, \textbf{Hamilton JJ}, Stevenson DM, Amador-Noguez, D, McMahon KD, and KT Forest. \emph{Genes from acI Actinobacteria Encode Synthesis Pathways for Retinal to Power Actinorhodopsin and a Complex Carotenoid}. In preparation.
%	\item Rohwer RR, \textbf{Hamilton JJ}, Newton, RJ, and KD McMahon. \emph{A Workflow which Leverages Ecosystem-Specific Databases to Achieve Fine-Level Taxonomic Resolution}. In preparation.
\end{etaremune}
* indicates an undergraduate student author

%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{etaremune}[itemsep=-2pt]
	\item Lawson CE, Wu S, Bhattacharjee AS, \textbf{Hamilton JJ}, McMahon KD, Goel R, and DR Noguera. (2017) \emph{Metabolic network analysis reveals microbial community interactions in anammox granules}. Nature Communications. 8:15416. \href{https://www.nature.com/articles/ncomms15416}{doi:10.1038/ncomms15416}.
	\item \textbf{Hamilton JJ}, Calixto Contreras M*, and JL Reed. (2015) \emph{Thermodynamics and H$_2$ Transfer in a Methanogenic, Syntrophic Community.} PLoS Computational Biology. 11(7): e1004364. \href{http://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1004364}{doi:10.1371/journal.pcbi.1004364}.
	\item Vinay-Lara E, \textbf{Hamilton JJ}, Stahl B, Broadbent JR, Reed JL, and JL Steele. (2014) \emph{Genome-Scale Reconstruction of Metabolic Networks of Lactobacillus casei ATCC 334 and 12A}. PLoS ONE. 9(11): e110785. \href{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0110785}{doi:10.1371/journal.pone.0110785}.
	\item \textbf{Hamilton JJ} and JL Reed. (2014) \emph{Software platforms to facilitate reconstructing genome-scale metabolic networks}. Environmental Microbiology. 16(1): 49-59. \href{http://onlinelibrary.wiley.com/doi/10.1111/1462-2920.12312/abstract}{doi:10.1111/1462-2920.12312}.
	\item \textbf{Hamilton JJ}, Dwivedi V*, and JL Reed. (2013) \emph{Quantitative Assessment of Thermodynamic Constraints on the Solution Space of Genome-Scale Metabolic Models.} Biophysical Journal. 105(2): 512-522. \href{http://www.cell.com/biophysj/abstract/S0006-3495%2813%2900685-1}{doi:10.1016/j.bpj.2013.06.011}.
	\item \textbf{Hamilton JJ} and JL Reed. (2012) \emph{Identification of Functional Differences in Metabolic Networks Using Comparative Genomics and Constraint-Based Models}. PLoS ONE. 7(4): e34670. \href{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0034670}{doi:10.1371/journal.pone.0034670}.
\end{etaremune}
* indicates an undergraduate student author

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\resheading{Invited Seminars}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Oral Presentations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{etaremune}[itemsep=-2pt]
	\item \textbf{Hamilton JJ}, Garcia SL, Brown BS*, Oyserman BO, Moya F, Bertilsson S, Malmstrom RR, Forest KT, and KD McMahon. \emph{Microbial Ecosystems Biology: A Framework for Scaling from Genomes to Ecosystems}. Association of Environmental Engineering and Science Professors Research and Education Conference. Ann Arbor, MI, June 2017.
	\item \textbf{Hamilton JJ}. \emph{Diving Into Freshwater Microbial Genomes to Infer
Bacterial Traits}. Wisconsin Ecology 22nd Annual Fall Symposium. Madison, WI, October 2016.
%	\item \textbf{Hamilton JJ}, Garcia SL, Bendall ML, Brown BS, Stevens SLR, Bertilsson S, Forest KT, Malmstrom RR, Stepanauskas R, Tringe SG, Woyke T, and KD McMahon. \emph{Omics-Enabled Insights into the Metabolism of Freshwater Bacteria}. USDA - NIFA Fellows Program Project Directors' Meeting. Washington, D.C.. August 2016.
	\item \textbf{Hamilton JJ} and JL Reed. \emph{Thermodynamics and H$_2$ Transfer in a Methanogenic,
Syntrophic Community.} COBRA 2014: 3rd Conference on Constraint-Based Reconstruction and Analysis, Charlottesville, VA, May 2014.
	\item \textbf{Hamilton JJ} and JL Reed. \emph{Identification of Functional Differences in Cyanobacterial Metabolic Networks Using Constraint-Based Models.} American Society of Microbiology (ASM) General Meeting, Denver, CO, May 2013.
	\item \textbf{Hamilton JJ}, Dwivedi V, and JL Reed. \emph{Thermodynamics-Based Flux-Balance Analysis: Incorporation of Thermodynamic and Metabolomic Data Into Genome-Scale Constraint-Based Models.} American Institute of Chemical Engineers Annual Meeting, Pittsburgh, PA, October 2012.
	\item \textbf{Hamilton JJ} and JL Reed. \emph{Comparison of Microbial Metabolic Networks to Guide Background Strain Selection.} American Chemical Society National Meeting, San Diego, CA, March 2012.
	\item  \textbf{Hamilton JJ} and JL Reed. \emph{Genome Alignment and Pair-Wise Comparison of Microbial Metabolic Networks Identifies Novel Potential Drug Targets.} American Institute of Chemical Engineers Annual Meeting, Minneapolis, MN, October 2011.
\end{etaremune}

%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Poster Presentations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{etaremune}
%	\item \textbf{Hamilton JJ}, Garcia SL, Bendall ML, Brown BS, Stevens SLR, Bertilsson S, Forest KT, Malmstrom RR, Stepanauskas R, Tringe SG, Woyke T, and KD McMahon. Metabolic Network Analysis and Metatranscriptomics of a Cosmopolitan and Streamlined Freshwater Lineage. Water@UW-Madison Poster Session, UW-Madison, Madison, WI. October 2016.
%	\item \textbf{Hamilton JJ}, Garcia SL, Bendall ML, Brown BS, Stevens SLR, Bertilsson S, Forest KT, Malmstrom RR, Stepanauskas R, Tringe SG, Woyke T, and KD McMahon. Metabolic Network Analysis and Metatranscriptomics of a Cosmopolitan and Streamlined Freshwater Lineage. Raper Symposium, UW-Madison, Madison, WI. September 2016.
	\item \textbf{Hamilton JJ}, Garcia SL, Bendall ML, Brown BS, Stevens SLR, Bertilsson S, Forest KT, Malmstrom RR, Stepanauskas R, Tringe SG, Woyke T, and KD McMahon. \emph{Metabolic Network Analysis and Metatranscriptomics of a Cosmopolitan and Streamlined Freshwater Lineage}. 16th International Symposium on Microbial Ecology, Montreal, Canada. August 2016.
%	\item \textbf{Hamilton JJ}, Bendall M, Glavina del Rio T, Bertilsson S, Malmstrom R, Stepanauskas R, Tringe S, Woyke T, and KD McMahon. \emph{Ecological Niches of Freshwater Actinobacteria Revealed through Comparative Genomics and Reverse Ecology.} Raper Symposium, UW-Madison, Madison, WI. September 2015.
%	\item \textbf{Hamilton JJ}, Bendall M, Glavina del Rio T, Bertilsson S, Malmstrom R, Stepanauskas R, Tringe S, Woyke T, and KD McMahon. \emph{Ecological Niches of Freshwater Actinobacteria Revealed through Comparative Genomics and Reverse Ecology.} Molecular Genetics of Bacteria and Phages Meeting, Madison, WI. July 2015.
	\item \textbf{Hamilton JJ}, Bendall M, Glavina del Rio T, Bertilsson S, Malmstrom R, Stepanauskas R, Tringe S, Woyke T, and KD McMahon. \emph{Ecological Niches of Freshwater Actinobacteria Revealed through Comparative Genomics and Reverse Ecology.} Gordon Research Conference on Applied and Environmental Microbiology, Mount Holyoke College, South Hadley, MA. July 2015.
	\item \textbf{Hamilton JJ}, He S, Bendall M, Glavina del Rio T, Bertilsson S, Malmstrom R, Stepanauskas R, Tringe S, Woyke T, and KD McMahon. \emph{Ecological Niches of Uncultivated Freshwater Phyla Revealed Through Comparative Genomics.} UMX: 10th Annual Department of Energy Joint Genome Institute User Meeting, Walnut Creek, CA. March 2015.
	\item \textbf{Hamilton JJ} and JL Reed. \emph{Thermodynamics and H$_2$ Transfer in a Methanogenic,
Syntrophic Community.} COBRA 2014: 3rd Conference on Constraint-Based Reconstruction and Analysis, Charlottesville, VA. May 2014.
%	\item \textbf{Hamilton JJ} and JL Reed. \emph{Identification of Functional Differences in Metabolic Networks Using Comparative Genomics and Constraint-Based Models.} Hougen Symposium, UW-Madison, Madison, WI. May 2012.	
\end{etaremune}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Teaching Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item \ressubheading{Critical Analyses in Microbiology}{UW-Madison}{Instructor}{Spring 2016}
	\item \ressubheading{Environmental Microbiology}{UW-Madison}{Guest Lecturer}{Spring 2015, Spring 2017}
	\item \ressubheading{Computational Tools for Analyzing Microbial Metabolism}{ASM General Meeting}{Instructor}{May 2013}
	\item \ressubheading{Biochemical Engineering}{UW-Madison}{Guest Lecturer}{Fall 2011, Fall 2012, Fall 2015}
	\item  \ressubheading{Biochemical Engineering}{UW-Madison}{Teaching Assistant}{Fall 2011}
	\item \ressubheading{Mass Transfer Operations}{UW-Madison}{Teaching Assistant}{Spring 2011}
	\item \ressubheading{Organic Chemistry}{CWRU}{Supplemental Instructor}{Fall 2008}
	\item \ressubheading{Chemistry of Materials}{CWRU}{Supplemental Instructor}{Fall 2007, Spring 2008, Spring 2009}
\end{itemize}

%\newpage

%\begin{comment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Mentoring Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item  \ressubheading{Robin R. Rohwer}{UW-Madison}{Ph.D. Student}{Fall 2015 to present}
	\item  \ressubheading{Christopher E. Lawson}{UW-Madison}{Ph.D. Student}{Fall 2015 to present}

	\item  \ressubheading{Brittany S. Brown}{UW-Madison}{Undergraduate Student}{Summer 2015}
	\item  \ressubheading{Montserrat Calixto Contreras}{UW-Madison}{Undergraduate Student}{Fall 2013}
	\item  \ressubheading{Stan Anderson}{UW-Madison}{Undergraduate Student}{Spring 2012}
	\item \ressubheading{Vivek Dwivedi}{UW-Madison}{Undergraduate Student}{Summer 2011}
	\item \ressubheading{Emely Y. Medina Chapparo}{UW-Madison}{Undergraduate Student}{Summer 2010}
\end{itemize}
%\end{comment}

\begin{comment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Academic and Professional Service}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item Reviewer for the following journals:
		\begin{itemize}
			\item Biochemical Engineering Journal
			\item Frontiers in Environmental Science
			\item Journal of Bacteriology	
 			\item PLoS Computational Biology
 			\item PLoS ONE			
		\end{itemize}
%	\item Member of the following scholarly and professional societies:
%	\item \ressubheading{New Educators' Orientation}{UW-Madison}{Student Volunteer}{Fall 2011-Spring 2014}
\end{itemize}
\end{comment}

\newpage

\begin{comment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item Katherine D. McMahon\\
		Professor\\
		Department of Bacteriology \\
		Department of Civil and Environmental Engineering \\
		University of Wisconsin-Madison \\
		E-mail: tmcmahon@engr.wisc.edu \\
		Phone: 608-890-2836 \\
		
	\item Daniel R. Noguera \\
		Professor \\
		Department of Civil and Environmental Engineering \\
		University of Wisconsin-Madison \\
		E-mail: noguera@engr.wisc.edu \\
		Phone: (608) 263-7783 \\

	\item Jennifer L. Reed\\
		Associate Professor\\
		Department of Chemical and Biological Engineering \\
		University of Wisconsin-Madison \\
		E-mail: reed@engr.wisc.edu \\
		Phone: 608-262-0188 \\

	\item Jae-Hyuk Yu \\
		Professor \\
		Department of Bacteriology  \\
		Department of Genetics \\
		University of Wisconsin-Madison \\
		Phone: 608-262-4696 \\
		E-mail: jyu1@wisc.edu \\

	\item Brian F. Pfleger\\
		Associate Professor\\
		Department of Chemical and Biological Engineering \\
		University of Wisconsin-Madison \\
		E-mail: pfleger@engr.wisc.edu \\
		Phone: 608-890-1940 \\

	\item Christos T. Maravelias\\
		Professor\\
		Department of Chemical and Biological Engineering \\
		University of Wisconsin-Madison \\
		E-mail: christos@engr.wisc.edu \\
		Phone: 608-265-9026 \\
\end{itemize}
\end{comment}


\end{document}